---
title: "R Notebook"
output: html_notebook
---
```{r}
#plyr can be used to manipulate data frames
library(plyr)
library(dplyr)
#ggplot is good for plotting
library(ggplot2)
#lmerTest loads mixed effects regressions and according t/z-tests
library(lmerTest)
library(caret)
library(ROCR)
library(pscl)
library(GGally)
```

Load Data. Leaf only, with contrast levels determined using sensitivity experiment

```{r}
setwd('/Users/mehmetyoruten/Library/CloudStorage/OneDrive-bwedu/Documents/School/Master/CPI Lab/Thesis/Experiment/behavioral analyses/data/go/')

participantID = 'go'

# Choose your data set
df <- read.csv("go.csv", header = TRUE)
df <- df[,-1]
cont_df <- df[df$control == 1,]
df <- df[df$control == 0,]

# Scale cut no
#df <- df %>% mutate_at(c('cutNo'), ~(scale(.) %>% as.vector))
#cont_df <- cont_df %>% mutate_at(c('cutNo'), ~(scale(.) %>% as.vector))

# Converting into factor variables
df$blockNo<-as.factor(df$blockNo)
#df$cutNo<-as.factor(df$cutNo)
df$expTime<-as.factor(df$expTime)
df$control<-as.factor(df$control)
df$leaf<-as.factor(df$leaf)
df$keyCode<-as.factor(df$keyCode)


head(cont_df, 10)
```
#Regression on Test
Check for the effect of Cut Number and Exposure Time on accuracy

```{r}
m0 <- glm(correct ~ 1, data = df, family = "binomial")
m1 <- glm(correct ~ cutNo, data = df, family = "binomial")
m2 <- glm(correct ~ cutNo + expTime,  data = df, family = "binomial")
m3 <- glm(correct ~ cutNo*expTime , data = df, family = "binomial")
m4 <- glm(correct ~ intOrder*expTime + cutNo , data = df, family = "binomial")

anova(m0,m1,m2,m3,m4, test = "Chisq")
```

```{r}
summary(m3)
```

```{r}
m4 <- glm(correct ~ meanSegInt, data = df, family = "binomial")
sum_msi <- summary(m4)
coeff_oths2 <- data.frame(coefs = (sum_msi$coefficients[2,1]), std = (sum_msi$coefficients[2,2]))
  
m5 <- glm(correct ~ segSize, data = df, family = "binomial")
sum_size <- summary(m5)
coeff_oths2 <- rbind(coeff_oths2, sum_size$coefficients[2,1:2])

m6 <- glm(correct ~ segCentDist , data = df, family = "binomial")
sum_dist <- summary(m6)
coeff_oths2 <- rbind(coeff_oths2, sum_dist$coefficients[2,1:2])

m7 <- glm(correct ~ deltaInt , data = df, family = "binomial")
sum_deltaInt <- summary(m7)
coeff_oths2 <- rbind(coeff_oths2, sum_deltaInt$coefficients[2,1:2])


rownames(coeff_oths2) <- c('Avrg Seg. Intensity','Seg. Size','Seg. Distance','Seg. Intens. Diff.')
coeff_oths2$lb <- coeff_oths2$coefs - (coeff_oths2$std*1.96)
coeff_oths2$ub <- coeff_oths2$coefs + (coeff_oths2$std*1.96)


m8 <- glm(correct ~ cutNo*expTime + segSize + segCentDist + intDiff, data = df, family = "binomial")
sum_all_oths <- summary(m8)
coeff_oths <- data.frame(coefs = (sum_all_oths$coefficients[,1]), std = (sum_all_oths$coefficients[,2]))
coeff_oths$lb <- coeff_oths$coefs - (coeff_oths$std*1.96)
coeff_oths$ub <- coeff_oths$coefs + (coeff_oths$std*1.96)

anova(m4,m5,m6,m7,m8, test="Chisq")



```

```{r}
summary(m8)
```

```{r}
df %>%
  dplyr::select(segSize, segCentDist, intDiff, segNcut, meanSegInt, deltaInt, intOrder) %>%
  ggpairs()
```


```{r}
rownames(coeff_oths) <- c('Intercept','Cut No.', 'Exp. Time Long', 'Seg. Size','Seg. Distance','Seg. Intens. Diff.','CutNo:ExpTime')
level_order <- c('Intercept','Cut No.', 'Exp. Time Long', 'CutNo:ExpTime', 'Seg. Size','Seg. Distance','Seg. Intens. Diff.')
level_order <- rownames(coeff_oths) 

mainEffect <- c('Intercept','Cut No.', 'Exp. Time Long', 'CutNo:ExpTime')
otherEffect <-c('Seg. Size','Seg. Distance','Seg. Intens. Diff.')
  
ggplot(coeff_oths, aes(x=factor(row.names(coeff_oths), levels = level_order),coefs)) + 
      geom_errorbar(aes(ymin=lb,ymax=ub),width=0.2) +
      geom_point(size=1) + 
      theme_bw() +
      ylab(""~beta~" -Coefficients with 95%CI") +
      xlab("Predictors") + 
      theme_classic() + 
      theme(axis.title.y = element_text(size = 18), axis.text=element_text(size = 16), axis.title.x=element_blank(), axis.text.x = element_text(angle = 45, hjust = 1)) +
      geom_hline(yintercept = 0, linetype = "dashed")

filename = paste('figs/', participantID, '_test_all_coefficients.png', sep = "")
ggsave(filename = filename, width = 10, height = 5, device='png', dpi=300)

```


# Regressions on Control

Create coefficients data frame for plotting interactions

```{r}
cm4 <- glm(correct ~ meanSegInt, data = cont_df, family = "binomial")
sum_msi <- summary(cm4)
coeff_oths_my <- data.frame(coefs = (sum_msi$coefficients[2,1]), std = (sum_msi$coefficients[2,2]))
  
cm5 <- glm(correct ~ segSize, data = cont_df, family = "binomial")
sum_size <- summary(cm5)
coeff_oths_my <- rbind(coeff_oths_my, sum_size$coefficients[2,1:2])

cm6 <- glm(correct ~ segCentDist , data = cont_df, family = "binomial")
sum_dist <- summary(cm6)
coeff_oths_my <- rbind(coeff_oths_my, sum_dist$coefficients[2,1:2])

cm7 <- glm(correct ~ deltaInt , data = cont_df, family = "binomial")
sum_deltaInt <- summary(cm7)
coeff_oths_my <- rbind(coeff_oths_my, sum_deltaInt$coefficients[2,1:2])


rownames(coeff_oths_my) <- c('Avrg Seg. Intensity','Seg. Size','Seg. Distance','Seg. Intens. Diff.')
coeff_oths_my$lb <- coeff_oths_my$coefs - (coeff_oths_my$std*1.96)
coeff_oths_my$ub <- coeff_oths_my$coefs + (coeff_oths_my$std*1.96)


cm8 <- glm(correct ~ cutNo*expTime + segSize + segCentDist + intDiff , data = cont_df, family = "binomial")
sum_all_oths <- summary(cm8)
coeff_oths_sw_all <- data.frame(coefs = (sum_all_oths$coefficients[,1]), std = (sum_all_oths$coefficients[,2]))
coeff_oths_sw_all$lb <- coeff_oths_sw_all$coefs - (coeff_oths_sw_all$std*1.96)
coeff_oths_sw_all$ub <- coeff_oths_sw_all$coefs + (coeff_oths_sw_all$std*1.96)

anova(cm4,cm5,cm6,cm7,cm8, test="Chisq")
```
```{r}
summary(cm8)
```


```{r}
#coeff_oths_sw_all <- coeff_oths_my_all[2:5,]

#rownames(coeff_oths_sw_all) <- c('Intercept','Cut No.', 'Exp. Time Long','Avrg Seg. Intensity', 'Seg. Size','Seg. Distance','Seg. Intens. Diff.' )
rownames(coeff_oths_sw_all) <- c('Intercept','Cut No.', 'Exp. Time Long', 'Seg. Size','Seg. Distance','Seg. Intens. Diff.','CutNo:ExpTime')
level_order <- c('Intercept','Cut No.', 'Exp. Time Long', 'CutNo:ExpTime', 'Seg. Size','Seg. Distance','Seg. Intens. Diff.')
level_order <- rownames(coeff_oths) 

ggplot(coeff_oths_sw_all, aes(x=factor(row.names(coeff_oths_sw_all), levels = level_order),coefs)) + 
      geom_errorbar(aes(ymin=lb,ymax=ub),width=0.2) +
      geom_point(size=1) + 
      theme_bw() +
      ylab(""~beta~" -Coefficients with 95%CI") +
      xlab("Predictors") + 
      theme_classic() + 
      theme(axis.title.y = element_text(size = 18), axis.text=element_text(size = 16), axis.title.x=element_blank(), axis.text.x = element_text(angle = 45, hjust = 1)) +
      geom_hline(yintercept = 0, linetype = "dashed")
  
filename = paste('figs/', participantID, '_control_all_coefficients.png', sep = "")
ggsave(filename = filename, width = 10, height = 5, device='png', dpi=300)
```


```{r}
m0 <- glm(correct ~ 1, data = cont_df, family = "binomial")
m1 <- glm(correct ~ cutNo, data = cont_df, family = "binomial")
m2 <- glm(correct ~ cutNo + expTime,  data = cont_df, family = "binomial")
m3 <- glm(correct ~ cutNo*expTime , data = cont_df, family = "binomial")
m4 <- glm(correct ~ intOrder*expTime + cutNo , data = cont_df, family = "binomial")
m5 <- glm(correct ~ cutNo*expTime + cutNo + avgCrossCorr, data = cont_df, family = "binomial")


anova(m1,m2,m3,m4,m5, test="Chisq")
```

```{r}
summary(m4)
print(pscl::pR2(m4)["McFadden"])
print(caret::varImp(m4))
```

# CONTROL - Predict 
```{r}
#use 70% of dataset as training set and 30% as test set
sample <- sample(c(TRUE, FALSE), nrow(cont_df), replace=TRUE, prob=c(0.7,0.3))
train  <- cont_df[sample, ]
test   <- cont_df[!sample, ]

trained_model <- glm(correct ~ cutNo*expTime + intOrder + avgCrossCorr, data = train, family = "binomial")
# get probabilities of getting correct answers
pHat <- predict(trained_model, test ,type = 'response', interval = 'confidence')


jitter = position_jitter(width = 0, height = 0.085)

ggplot(test) +
  geom_point(aes(x=cutNo, y = pHat)) + 
  geom_point(aes(x=cutNo, y = correct, color=factor(correct)), position = jitter)
```
Sensitivity (True Positive Rate)
Specificity (True Negative Rate)

```{r}
test_correct <- as.factor(test$correct)
cutOffAll <- seq(0.5, 0.95, by=0.01)
sensArray <- c(0)
specArray <- c(0)

for (i in 1:length(cutOffAll))
  {
  cutOff <- cutOffAll[i]
  predicted <- ifelse(pHat > cutOff, 1, 0)
  predicted <- as.factor(predicted)
  sens = sensitivity(test_correct, predicted)
  spec = specificity(test_correct, predicted)
  sensArray[i] = sens
  specArray[i] = spec
}

optCOid = which.min(specArray - sensArray)
optCutOff = cutOffAll[optCOid]
sens_spec <- data.frame(cutOffAll,sensArray, specArray)


ggplot(data = sens_spec) + 
  geom_line(aes(x=cutOffAll, y = sensArray)) + 
  geom_line(aes(x=cutOffAll, y = specArray), color = 'red') +
  scale_y_continuous(sec.axis = sec_axis(~., name = "Specificity")) +
  theme_bw() +
  ylab("Sensitivity") +
  xlab("Cut Off") + 
  theme_classic() +
  theme(axis.title.y.right = element_text(colour = "red"), legend.position="none") +
  geom_vline(xintercept = optCutOff, linetype = "dashed")
```

```{r}
predicted <- ifelse(pHat > optCutOff, 1, 0)
predicted <- as.factor(predicted)
confMat <- confusionMatrix(predicted,test_correct)
accuracy <- (confMat$table[1]+confMat$table[4]) / sum(confMat$table)
print(confMat)
```



# TEST - Predict 
```{r}
#use 70% of dataset as training set and 30% as test set
sample <- sample(c(TRUE, FALSE), nrow(df), replace=TRUE, prob=c(0.7,0.3))
train  <- df[sample, ]
test   <- df[!sample, ]

trained_model <- glm(correct ~ cutNo*expTime, data = train, family = "binomial")
# get probabilities of getting correct answers
pHat <- predict(trained_model, test ,type = 'response', interval = 'confidence')

jitter = position_jitter(width = 0, height = 0.085)

ggplot(test) +
  geom_point(aes(x=cutNo, y = pHat)) + 
  geom_point(aes(x=cutNo, y = correct, color=factor(correct)), position = jitter)
```
Sensitivity (True Positive Rate)
Specificity (True Negative Rate)

```{r}
test_correct <- as.factor(test$correct)
cutOffAll <- seq(0.5, 0.95, by=0.01)
sensArray <- c(0)
specArray <- c(0)

for (i in 1:length(cutOffAll))
  {
  cutOff <- cutOffAll[i]
  predicted <- ifelse(pHat > cutOff, 1, 0)
  predicted <- as.factor(predicted)
  sens = sensitivity(test_correct, predicted)
  spec = specificity(test_correct, predicted)
  sensArray[i] = sens
  specArray[i] = spec
}

optCOid = which.min(specArray - sensArray)
optCutOff = cutOffAll[optCOid]
sens_spec <- data.frame(cutOffAll,sensArray, specArray)


ggplot(data = sens_spec) + 
  geom_line(aes(x=cutOffAll, y = sensArray)) + 
  geom_line(aes(x=cutOffAll, y = specArray), color = 'red') +
  scale_y_continuous(sec.axis = sec_axis(~., name = "Specificity")) +
  theme_bw() +
  ylab("Sensitivity") +
  xlab("Cut Off") + 
  theme_classic() +
  theme(axis.title.y.right = element_text(colour = "red"), legend.position="none") +
  geom_vline(xintercept = optCutOff, linetype = "dashed")
```

```{r}
predicted <- ifelse(pHat > optCutOff, 1, 0)
predicted <- as.factor(predicted)
confMat <- confusionMatrix(predicted,test_correct)
accuracy <- (confMat$table[1]+confMat$table[4]) / sum(confMat$table)
print(confMat)
```

```{r}

```

